Redundant calibration as a complex optimization problem

### 2016-12-09 paper.tex
added kappa and itr plots

\subsubsection{Spectral Condition Number}
kappa + itr plots
\subsubsection{Sparsity}

>>>>

\subsubsection{Spectral Condition Number}
kappa + itr plots
\begin{figure*}
\centering
\subfigure[$\kappa$]{\includegraphics[width=0.47\textwidth]{./kappa.pdf}\label{fig:kappa}}
% V_R_3.pdf: 585x441 pixel, 72dpi, 20.64x15.56 cm, bb=0 0 585 441
\subfigure[Iterations required before and after Preconditioning]{\includegraphics[width=0.47\textwidth]{./cg_itr.pdf}\label{fig:cg_itr}}
\caption{The graphs presented here were generated using the second experimental setup in Table~\ref{tab:ch_parm}. In the left panel we have plotted the spectral condition number $\kappa$ of the Hessian $\bH$, before (magenta and red curves) and after preconditioning (blue curve), at different SNR values as a function of the
number of antennas $N$ in the array. This plot shows us that we can drastically reduce the condition number of $\bH$ by preconditioning. Moreover, $\kappa$ is also
independent of the problem size (the number of antennas in the array). The fact that $\kappa$ is small and independent of problem size implies that it simply drops out 
of Eq.~\eqref{eq:cg_bound}. The right hand panel confirms this result. In the right hand panel we have plotted the number of major iterations (line 6 of Algorithm \ref{algo:CG})) required by the conjugate 
gradient method to invert $\bH$, before (magenta and red curves) and after preconditioning (blue and green curves), at different SNR values as a function of the number of antennas $N$ in the array.  
method. The right hand panel shows us that the number of major iterations needed by the preconditioned conjugate gradient method to invert $\bH$ is much smaller than the 
dimension of $\bH$ and is independent of the problem size (the number of antennas in the array). 
\label{fig:sup_anti}} 
\end{figure*}

\subsubsection{Sparsity}
